QSO decomposition

### 2018-11-27 manuscript/manuscript.tex
re-fitting CID206 with 41 frame size, paper writing with more figures

\section{Introduction}
\label{sec:introduction}
skeleton
\\
1. The ML relation and why understand its evolution is important.\\
2. To understand this evolution, it is important to trace to high redshift. So, why it is difficult.\\
3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...\\
4. This work, we introduces samples till redshift 1.7.

@@

In figure, we demonstrate the optimized result of each system inferred by \lenstronomy. We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}.

@@

We list all the inference of the host galaxy properties in the Table.

@@

We summarized the homogenized R-band luminosities
in Table?

@@

With the self-consistent cross-calibration, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two. We summarized the inference of the \mbh\ together with the details on the emission line in Table.

\section{Results}
\label{sec:result}
\subsection{M-L relation}
\subsubsection{Stellar mass estimates}
stellar mass \\
\subsection{M-M$_*$ relation}

@@

\section*{Acknowledgments}
We thank the people who discuss with the paper. X.D. acknowledges support by China Postdoctoral Science Foundation Funded Project; he is also grateful for Zong-Hong Zhu's support and funding. T.T. acknowledges support by the Packard Foundation in the form of a Packard Research Fellowship.

@@

\begin{deluxetable*}{llccc}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{The sample information for the 32 systems.} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W$^*$ & 150.2789 & 1.9595\\
COSMOS-CID1281 & 1.445 & ??? & 150.4160 & 2.5258\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
COSMOS-CID216 & 1.567 & F140W$^*$ & 149.7918 & 1.8729\\
COSMOS-CID237 & 1.618 & F140W$^*$ & 149.9916 & 1.7243\\
COSMOS-CID255 & 1.664 & ???$^*$ & 150.1017 & 1.8483\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
COSMOS-CID452 & 1.407 & F125W$^*$ & 150.0045 & 2.2371\\
COSMOS-CID454 & 1.478 & F140W$^*$ & 149.8681 & 2.3307\\
COSMOS-CID50 & 1.239 & F125W$^*$ & 150.2080 & 2.0833\\
COSMOS-CID543 & 1.301 & F125W$^*$ & 150.4519 & 2.1448\\
COSMOS-CID597 & 1.272 & ???$^*$ & 150.5262 & 2.2449\\
COSMOS-CID607 & 1.294 & F125W$^*$ & 150.6097 & 2.3231\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
COSMOS-LID1538 & 1.527 & F140W$^*$ & 150.6215 & 2.1588\\
COSMOS-LID360 & 1.579 & F140W$^*$ & 150.1251 & 2.8617\\
COSMOS-XID2138 & 1.551 & F140W$^*$ & 149.7036 & 2.5781\\
COSMOS-XID2202 & 1.516 & F140W$^*$ & 150.6530 & 1.9969\\
COSMOS-XID2396 & 1.600 & F140W$^*$ & 149.4779 & 2.6425\\
CDFS-1 & 1.630 & F140W$^*$ & 52.8990 & -27.8600\\ 
CDFS-229 & 1.326 & F125W$^*$ & 53.0680 & -27.6580\\ 
CDFS-321 & 1.570 & F140W$^*$ & 53.0486 & -27.6239\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
}
\end{deluxetable*}

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The process of weighting for COSMOS-CID1174 } 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
\hline\\
Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
The detailed information of the weights for the inference of CID1174. The inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

{@{\extracolsep{4pt}}lcccccccc}   % need for the gap between the clines.

@@

\tablecaption{The sample information for the 32 systems.} 

@@

\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude}\\

@@

\colhead{}& \colhead{(AB system)} \\

@@

\colhead{(8)}& \colhead{(9)}

@@

Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The inference of the \mbh\ for the 32 systems.} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\lambda \rm L _{H\alpha}$}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\lambda \rm L _{\lambda5100}$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{($10^{42}{\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{($10^{44}{\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.807 & 5898.264 & 44.76243 & 8.818 \\
CID1281 & 1619.4891 & 43.23945 & 7.559 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.62 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.127 & 3709.241 & 45.37122 & 8.731 \\
CID3242 & 2543.2202 & 43.83323 & 8.278 & 3774.503 & 45.09891 & 8.605 \\
CID3570 & 1958.8551 & 43.16374 & 7.683 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
CID454 & 2824.2693 & 43.34466 & 8.1 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
CID543 & 2188.8447 & 43.57404 & 8.005 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.629 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.335 & 4241.526 & 44.78209 & 8.542 \\
CID70 & 2480.4058 & 43.50531 & 8.076 & 3981.8574 & 45.1582 & 8.682 \\
LID1273 & 3223.8484 & 43.61001 & 8.361 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.274 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.283 & 2868.8992 & 45.08676 & 8.36 \\
XID2138 & 3185.8613 & 43.6148 & 8.354 & 2944.7766 & 44.80782 & 8.239 \\
XID2202 & 2973.2378 & 43.56249 & 8.265 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.306 & 2657.8386 & 45.50467 & 8.51 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.294 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 7.927 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
SXDS-X50 & 1816.672 & 43.421 & 7.759 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 7.97 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.267 & 4508.5146 & 44.51285 & 8.456 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.006 & 1695.7146 & 45.05337 & 7.886 \\
\enddata
\label{tab:result_sersic}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
}
\end{deluxetable*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
\caption{\label{fig:ML} WFC3 F110W images for 12 objects. In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name. All images are $10.8\arcsec\times10.8\arcsec$ in size and
 displayed with an inverted asinh stretch.
	    The fourth column shows the corresponding one-dimensional surface brightness profiles. In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown. Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel. Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.}
}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3570_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID452_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
}
\figurenum{1}
\caption{\label{fig:ML} Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
}
\figurenum{1}
\caption{\label{fig:ML} Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1273_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
}
\figurenum{1}
\caption{\label{fig:ML} Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
}
\figurenum{1}
\caption{\label{fig:ML} Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
}
\figurenum{1}
\caption{\label{fig:ML} Continued.}
\end{figure*}

>>>>

\section{Introduction}
\label{sec:introduction}
skeleton of introduction
\\
1. Introduce the ML relation and why understand its evolution is important.\\
2. To understand this evolution, it is important to trace to high redshift. Why it is difficult.\\
3. Introduce reference. Woo's. SS13, Treu's, Park79. In the theory, DeGraf...Highlight the redshift range $z>1.2$\\
4. In this paper, we study the ML relation up to redshift 1.7.

@@

In Figure~\ref{fig:QSO_decomp}, we demonstrate the optimized result of each system inferred by \lenstronomy. We also show the weighting process for an example system -- CID1174 in Table~\ref{tab:weight_CID1174}. In Figure~\ref{fig:flux_r_n_corner}, we summarize the relation among the inferred values of: \Reff, \sersic\ $n$, and host to total flux ratio.

@@

We list all the inference of the host galaxy properties in the Table~\ref{tab:result_sersic}.

@@

\textcolor{blue}{Introduce the passive evolution?}
To directly compare with local samples, we consider the passive evolution scenario for the inferred \lhost\ and transfer to its expected value at today.

We summarized the homogenized R-band luminosities
in Table~\ref{tab:result_sersic}.

@@

With the self-consistent cross-calibration, we estimate the \mbh\ by adopting the emission line properties measured by \citet{Schulze2018}. For the system with both \halpha\ and \hbeta\ emission line information, we adopt the average \mbh\ value by these two. We summarized the inference of the \mbh\ together with the details on the emission line in Table~\ref{tab:result_mbh}.

\section{Results}
\label{sec:result}
\subsection{\mbh-\lhost\ relation}

\subsection{\mbh-M$_*$ relation}
\subsubsection{Stellar mass estimates}
stellar mass \\

@@

\section{discuss}
\label{sec:dis}
\subsection{Systematic error}
\subsection{Fitting mask for CID1174 and ECDFS-358}

\section*{Acknowledgments}
We thank the people who discuss with the paper.

@@

\begin{deluxetable}{llccc}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{The sample information for the 32 systems.} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W$^*$ & 150.2789 & 1.9595\\
COSMOS-CID1281 & 1.445 & ??? & 150.4160 & 2.5258\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088\\
COSMOS-CID216 & 1.567 & F140W$^*$ & 149.7918 & 1.8729\\
COSMOS-CID237 & 1.618 & F140W$^*$ & 149.9916 & 1.7243\\
COSMOS-CID255 & 1.664 & ???$^*$ & 150.1017 & 1.8483\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076\\
COSMOS-CID452 & 1.407 & F125W$^*$ & 150.0045 & 2.2371\\
COSMOS-CID454 & 1.478 & F140W$^*$ & 149.8681 & 2.3307\\
COSMOS-CID50 & 1.239 & F125W$^*$ & 150.2080 & 2.0833\\
COSMOS-CID543 & 1.301 & F125W$^*$ & 150.4519 & 2.1448\\
COSMOS-CID597 & 1.272 & ???$^*$ & 150.5262 & 2.2449\\
COSMOS-CID607 & 1.294 & F125W$^*$ & 150.6097 & 2.3231\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275\\
COSMOS-LID1538 & 1.527 & F140W$^*$ & 150.6215 & 2.1588\\
COSMOS-LID360 & 1.579 & F140W$^*$ & 150.1251 & 2.8617\\
COSMOS-XID2138 & 1.551 & F140W$^*$ & 149.7036 & 2.5781\\
COSMOS-XID2202 & 1.516 & F140W$^*$ & 150.6530 & 1.9969\\
COSMOS-XID2396 & 1.600 & F140W$^*$ & 149.4779 & 2.6425\\
CDFS-1 & 1.630 & F140W$^*$ & 52.8990 & -27.8600\\ 
CDFS-229 & 1.326 & F125W$^*$ & 53.0680 & -27.6580\\ 
CDFS-321 & 1.570 & F140W$^*$ & 53.0486 & -27.6239\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: HST filter by WFC3. The marker $^*$ indicate the corresponding sample also has the ACS/F814W image.
Column 4 and 5: The $RA$ and $DEC$ of the system.
}
\end{deluxetable}

\begin{deluxetable*}{ccccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of the weighting for the inference of CID1174. } 
\tablehead{ 
\colhead{PSF rank} &
\colhead{total $\chi ^2$} & 
\colhead{weights $w_i$} &
\colhead{host flux (counts)} &
\colhead{host flux ratio}&
\colhead{\Reff (arcsec)}&
\colhead{\sersic\ $n$}
 \\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)} 
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
1 & 8646.711 & 1.000 & 99.102 & 41.9\% & 0\farcs{}298 & 1.932 \\
2 & 8816.947 & 0.849 & 76.740 & 33.0\% & 0\farcs{}365 & 1.102 \\
3 & 9304.841 & 0.530 & 128.618 & 54.7\% & 0\farcs{}231 & 2.780 \\
4 & 9652.575 & 0.379 & 187.498 & 79.0\% & 0\farcs{}116 & 6.175 \\
5 & 10018.324 & 0.267 & 75.061 & 32.3\%& 0\farcs{}365 & 1.226 \\
6 & 10087.456 & 0.249 & 79.835 & 34.3\% & 0\farcs{}358 & 1.195 \\
7 & 10457.811 & 0.174 & 108.580 & 46.4\% & 0\farcs{}262 & 2.190 \\
8 & 10721.421 & 0.135 & 63.994 & 27.8\% & 0\farcs{}406 & 0.720 \\
\hline\\
Weighted value & & & 103.534 $\pm$ 34.267 & 44.0\%$\pm$14.2\%& 0\farcs{}296$\pm$0\farcs{}079 & 2.173$\pm$1.500  \\
\enddata
\label{tab:weight_CID1174}
\tablecomments{
Column~1: The rank of the PSF from the library.
Column~2: Total $\chi ^2$ for the corresponding PSF.
Column~3: Weights for co-adding the inference.
Column~4-7: Fitted value for the host flux, host/total flux ratio, effective radius, and \sersic\ index.
For this sample, the inflation value $\alpha$ calculated by Eq.~\ref{eq:alpha} is 16.671.
}
\end{deluxetable*}

@@

{@{\extracolsep{4pt}}lccccccccc}   % need for the gap between the clines.

@@

\tablecaption{The inference of the host information by the QSO decomposition for the 32 systems.} 

@@

\colhead{reduced $\chi ^2$}& \colhead{host flux ratio}& \colhead{magnitude} & \colhead{$\log L_R$}\\

@@

\colhead{}& \colhead{(AB system)}&\colhead{($L_{\odot,R}$)} \\

@@

\colhead{(8)}& \colhead{(9)}&\colhead{(10)}

@@

Column~1: Object ID.
Column~2: Reduced $\chi ^2$ value by the best PSF in the library.
Column~3-6: Host inference by the WFC3 image.
Column~7-9: Host inference by the ACS image. 
Column~10: The inferred host Luminosity in the rest-frame R band.

@@

\begin{deluxetable*}
{@{\extracolsep{4pt}}lcccccc}   % need for the gap between the clines.
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{The inference of the \mbh\ for the 32 systems.} 
\tablehead
{ 
\colhead{Target ID}&
  \multicolumn{3}{c}{using emission line \halpha}&
  \multicolumn{3}{c}{using emission line \hbeta} \\
  \cline{2-4}  \cline{5-7} \\
\colhead{}& 
\colhead{FWHM}& \colhead{$\log(\lambda \rm L _{H\alpha}$)}& \colhead{\mbh}&
\colhead{FWHM(5100)}& \colhead{$\log(\lambda \rm L _{\lambda5100})$}& \colhead{\mbh}\\
\colhead{}& 
\colhead{(\kms)}& \colhead{(${\rm erg~s^{-1}}$)}& 
\colhead{(M$_{\odot}$)}& \colhead{(\kms)}& 
\colhead{(${\rm erg~s^{-1}}$)}&\colhead{(M$_{\odot}$)}\\
\colhead{(1)}& 
\colhead{(2)}& \colhead{(3)}& 
\colhead{(4)}& \colhead{(5)}& 
\colhead{(6)}&\colhead{(7)}
}
\startdata 
CID1174 & 1906.3037 & 43.43237 & 7.807 & 5898.264 & 44.76243 & 8.818 \\
CID1281 & 1619.4891 & 43.23945 & 7.559 & ... & ... & ... \\
CID206 & 3333.5527 & 43.4776 & 8.317 & ... & ... & ... \\
CID216 & 2229.5232 & 42.84509 & 7.620 & ... & ... & ... \\
CID237 & 2112.3306 & 43.85546 & 8.129 & ... & ... & ... \\
CID255 & 1932.0933 & 43.9924 & 8.127 & 3709.241 & 45.37122 & 8.731 \\
CID3242 & 2543.2202 & 43.83323 & 8.278 & 3774.503 & 45.09891 & 8.605 \\
CID3570 & 1958.8551 & 43.16374 & 7.683 & ... & ... & ... \\
CID452 & 3457.8801 & 42.92298 & 8.044 & 3127.3306 & 44.63353 & 8.201 \\
CID454 & 2824.2693 & 43.34466 & 8.100 & ... & ... & ... \\
CID50 & 2339.9104 & 43.93786 & 8.263 & 1938.5676 & 45.32766 & 8.145 \\
CID543 & 2188.8447 & 43.57404 & 8.005 & ... & ... & ... \\
CID597 & 1656.3296 & 43.32955 & 7.629 & ... & ... & ... \\
CID607 & 3009.1816 & 43.67079 & 8.335 & 4241.526 & 44.78209 & 8.542 \\
CID70 & 2480.4058 & 43.50531 & 8.076 & 3981.8574 & 45.1582 & 8.682 \\
LID1273 & 3223.8484 & 43.61001 & 8.361 & ... & ... & ... \\
LID1538 & 2941.422 & 43.59594 & 8.274 & ... & ... & ... \\
LID360 & 2481.7253 & 43.88091 & 8.283 & 2868.8992 & 45.08676 & 8.36 \\
XID2138 & 3185.8613 & 43.6148 & 8.354 & 2944.7766 & 44.80782 & 8.239 \\
XID2202 & 2973.2378 & 43.56249 & 8.265 & ... & ... & ... \\
XID2396 & 2271.2617 & 44.06196 & 8.306 & 2657.8386 & 45.50467 & 8.51 \\
CDFS-1 & ... & ... & ... & ... & ... & ... \\
CDFS-229 & ... & ... & ... & ... & ... & ... \\
CDFS-321 & 2441.93 & 43.92714 & 8.294 & ... & ... & ... \\
CDFS-724 & ... & ... & ... & ... & ... & ... \\
ECDFS-358 & 2237.2314 & 43.39674 & 7.927 & ... & ... & ... \\
SXDS-X1136 & 2759.8953 & 43.43305 & 8.129 & 6761.222 & 44.71429 & 8.912 \\
SXDS-X50 & 1816.672 & 43.42100 & 7.759 & ... & ... & ... \\
SXDS-X717 & 2930.7417 & 43.04988 & 7.970 & ... & ... & ... \\
SXDS-X735 & 2702.0962 & 43.69804 & 8.256 & 3519.6052 & 45.07463 & 8.532 \\
SXDS-X763 & 2961.1743 & 43.57321 & 8.267 & 4508.5146 & 44.51285 & 8.456 \\
SXDS-X969 & 2296.0566 & 43.50066 & 8.006 & 1695.7146 & 45.05337 & 7.886 \\
\enddata
\label{tab:result_mbh}
\tablecomments{
Column 1: Object ID.
Column 2: .
Column 3: HST filter. The samples with marker $^*$ have the ACS/F814W.
}
\end{deluxetable*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID206_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID216_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID237_SB_profile.pdf}
\caption{\label{fig:QSO_decomp} 
\textcolor{red}{need to be written:}
%WFC3 images for 12 objects. In each row, observed data (first column), best-fit models (second column), and residuals (third column) are presented with the object name. All images are $10.8\arcsec\times10.8\arcsec$ in size and  displayed with an inverted asinh stretch. The fourth column shows the corresponding one-dimensional surface brightness profiles. In each top panel, the profiles measured from the data (open circles), the best-fit model (black solid line), and the sub-components of the model for bulge (blue solid line), disk (green solid line), AGN (red solid line) are shown. Residuals (gray circles), the difference of the profiles between the data and the best-fit model, are presented in each bottom panel. Note that the one-dimensional surface brightness profiles are shown for illustration purposes only, the actual fitting made use of the full two-dimensional images.
}}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3242_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID3570_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID452_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID454_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID50_SB_profile.pdf}
}
\figurenum{1}
\caption{Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID543_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID607_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID70_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2138_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2202_SB_profile.pdf}
}
\figurenum{1}
\caption{Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_XID2396_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1273_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID1538_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_LID360_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X1136_SB_profile.pdf}
}
\figurenum{1}
\caption{Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X50_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X717_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X735_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X763_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_SXDS-X969_SB_profile.pdf}
}
\figurenum{1}
\caption{Continued.}
\end{figure*}

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-1_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-229_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-321_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_CDFS-724_SB_profile.pdf}
\includegraphics[height=0.25\textwidth]{fig/best_fit_ECDFS-358_SB_profile.pdf}
}
\figurenum{1}
\caption{Continued.}
\end{figure*}

\begin{figure*}
\centering
{
\includegraphics[height=0.75\textwidth]{fig/flux_r_n_corner.pdf}
}
\caption{\label{fig:flux_r_n_corner} The relations among these values.}
\end{figure*}
